Handling String-Number Conversion in String Constraint Solving

### 2019-10-02 draft.tex
update

\documentclass{llncs}

@@

\title{Handling String-Number Conversion in String Constraint Solving}
\author{}
\institute{}

@@

\begin{figure}
	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
	\begin{tikzpicture} 
		\node[state,initial] (q0)  {$\st{0}{0}$};
		\node[state] (q1) [right = 3cm of q0] {$\st{1}{0}$};
		\node (q2) [right = 1.8cm of q1]{};
		\node (q3) [right = 1cm of q2]{};
		\node[state,accepting] (qm) [right = 1.8cm of q3] {$\st{m}{0}$};

@@

  		\draw[->] (q1) edge [bend left] node [left]{$\sym{1}{0}$} (q11) ;
		\draw[->] (q11) edge [bend left] node [above]{$\sym{1}{1}$} (q12) ;
		\draw[->] (q12) edge [bend left] node [right]{$\sym{1}{2}$} (q1) ;
	\end{tikzpicture} 
	\label{fig:sfa_def}
	\caption{An example of a symbolic flat automaton}
\end{figure}

@@

\begin{figure}
	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}

@@

	\caption{Symbolic flat automata of $x$, $y$, $xy$ and $yx$}
	\label{fig:sfa}
\end{figure}

@@

\begin{itemize}
\item If $(q_1,v_i^{(j)},q_2) \in T$, then for all $p\in P,((q_1,p),(v_i^{(j)},\epsilon),(q_2,p))\in T^2$.
\item If $(p_1,v_i^{(j)},p_2) \in T'$, then for all $q\in Q,((q,p_1),(\epsilon,v_i^{(j)}),(q,p_2))\in T^2$.
\item If $(q_1,v_i^{(j)},q_2) \in T$ and $(p_1,v_{i'}^{(j')},p_2) \in T'$, then $((q_1,p_1),(v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))\in T^2$.
\end{itemize}	
The first two cases correspond to the situation when the character variable $v_i^{(j)}$ is assigned $\epsilon$. In such cases, only one automaton changes its state.

@@

For the case that $n$ is a positive integer, the value of $n$ can be characterized by a linear constraint $n= (v_0\times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0)-1})$.
Observe that when $\#(v_0)=1$, the loop is taken only once and we have $n=v_0\times 10+ v_1$. When $\#(v_0)=2$, the loop is taken twice and we have 
$n=(v_0\times 10+ v_1) + ( v_0\times 10+ v_1)\times 100$.

>>>>

\documentclass[sigplan,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

\title{Handling String-Number Conversion in String Constraint Solving}
\author{}

@@

\begin{figure*}
	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
	\begin{tikzpicture} 
		\node[state,initial] (q0)  {$\st{0}{0}$};
		\node[state] (q1) [right = 3cm of q0] {$\st{1}{0}$};
		\node (q2) [right = 1.8cm of q1]{};
		\node (q3) [right = 1cm of q2]{};
		\node[state,accepting] (qm) [right = 1.8cm of q3] {$\st{m}{0}$};

@@

  		\draw[->] (q1) edge [bend left] node [left]{$\sym{1}{0}$} (q11) ;
		\draw[->] (q11) edge [bend left] node [above]{$\sym{1}{1}$} (q12) ;
		\draw[->] (q12) edge [bend left] node [right]{$\sym{1}{2}$} (q1) ;
	\end{tikzpicture} 
	\label{fig:sfa_def}
	\caption{An example of a symbolic flat automaton}
\end{figure*}

@@

\begin{figure*}
	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}

@@

	\caption{Symbolic flat automata of $x$, $y$, $xy$ and $yx$}
	\label{fig:sfa}
\end{figure*}

@@

\begin{itemize}
\item If $(q_1,v_i^{(j)},q_2) \in T$, then for all states $p\in P$, we have $((q_1,p),(v_i^{(j)},\epsilon),(q_2,p))\in T^2$.
\item If $(p_1,v_i^{(j)},p_2) \in T'$, then for all states $q\in Q,((q,p_1)$, we have $(\epsilon,v_i^{(j)}),(q,p_2))\in T^2$.
\item If $(q_1,v_i^{(j)},q_2) \in T$ and $(p_1,v_{i'}^{(j')},p_2) \in T'$, then we have $((q_1,p_1),(v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))\in T^2$.
\end{itemize}	
The first two cases correspond to the situation when the character variable $v_i^{(j)}$ is assigned $\epsilon$. In such cases, only one automaton changes its state.

@@

For the case that $n$ is a positive integer, the value of $n$ can be characterized by a constraint $n= (v_0\times 10+ v_1) \times (1+100 +100^2 + \ldots 100 ^{\#(v_0)-1})=  (v_0\times 10+ v_1) \times \frac{100^{\#(v_0)}}{100-1}$. 
The constraint uses $\#(v_0)$ to capture the total number of loop traversal.
